### 2019-05-22 4_implementation.tex
A lot of edits to shrink section 4.

Spark~\cite{Spark10} is an implicitly-parallel programming model for
large scale data analytics. As
one of the programming models in this study not originally intended
for scientific computing, Spark makes very different tradeoffs from
other systems under consideration, and therefore makes an interesting
point of comparison.

The core abstractions in Spark are functional operators such as map,
reduce, filter, join, etc. Functions in Spark operate on
\emph{resilient
  distributed datasets} (RDDs), which are globally-visible,
dynamically single-assignment data structures. One of Spark's primary
optimizations is the caching of RDDs to avoid unnecessary
disk traffic.

Though Spark has tasks internally, these are not exposed to the user,
so one of the challenges in developing a Task Bench implementation is
mapping the task graph to a set of operators that result in the
desired performance behavior. We use a combination of
\lstinline[language=Scala]{flatMap} and
\lstinline[language=Scala]{groupByKey} operations to generate task
dependencies, and then \lstinline[language=Scala]{mapPartitions} to execute a
series of tasks. We use an explicit hash partitioner to ensure that
Spark does not attempt to group multiple Task Bench tasks into a
single Spark task, as the tasks in Task Bench already represent coarse-grained units of work.

We performed extensive experiments to verify that no
extraneous factors interfered with our Spark measurements. We
completely disabled logging, ensured no RDDs are written
to disk, confirmed there is no measurable overhead due to JNI
calls from Java to C or due to the serialization of data structures, and cross-checked results with known cases
that hit optimal task throughput in Spark.

@@

StarPU~\cite{StarPU11} is a task-based system that supports a \emph{sequential task flow} (STF)
programming model similar to PaRSEC's DTD. Our Task Bench implementation in
StarPU is very similar to PaRSEC, including the use of a switch
statement to handle dynamic numbers of task dependencies and manual
elision of tasks on unrelated nodes to improve scalability.
We use a simplified version of the 2D block cyclic data distribution from the Chameleon 
project~\cite{Chameleon}.

@@

TensorFlow~\cite{TensorFlow15} is a programming system designed for
deep learning workloads. Although TensorFlow's API exposes
machine learning concepts, internally TensorFlow is a task graph execution engine, making it a good fit for
Task Bench. TensorFlow programs are written by creating nodes in the
task graph, and then connecting these nodes with edges to implement
the desired dataflow. Task graphs are composed in a high-level
language such as Python, but then serialized and run by an
execution engine written in C++.

Our Task Bench implementation in TensorFlow works by defining a custom
operator, which we instantiate for each point in the task graph. We
then define dataflow edges to correspond to the task dependencies.

>>>>

Spark~\cite{Spark10} is an implicitly-parallel programming model for
large scale data analytics.
The core abstractions in Spark are functional operators such as map,
reduce, and join. Data in Spark are stored in
\emph{resilient
  distributed datasets} (RDDs): globally-visible,
dynamically single-assignment data structures. Spark caches RDDs in memory to avoid unnecessary
disk traffic.

Spark has tasks internally but they are not exposed to the user,
so a Task Bench implementation must map the task graph to a set of operators that result in the
desired execution. We use
\lstinline[language=Scala]{flatMap} and
\lstinline[language=Scala]{groupByKey} to generate task
dependencies, and then \lstinline[language=Scala]{mapPartitions} to execute a
series of tasks. An explicit hash partitioner ensures that
Spark does not attempt to group multiple Task Bench tasks into a
single Spark task, as tasks in Task Bench already represent coarse-grained units of work.

We performed extensive experiments to verify that no
extraneous factors interfered with our Spark measurements. We
disabled logging, ensured no RDDs are written
to disk, confirmed there is no measurable overhead due to JNI
calls from Java to C or due to the serialization of data structures, and cross-checked results with known cases
that hit optimal task throughput in Spark.

@@

StarPU~\cite{StarPU11} is a task-based system that supports a \emph{sequential task flow} (STF)
programming model similar to PaRSEC's DTD. Our Task Bench implementation in
StarPU is very similar to PaRSEC.
%% We use a simplified version of the 2D block cyclic data distribution from the Chameleon 
%% project~\cite{Chameleon}.

@@

TensorFlow~\cite{TensorFlow15} is a programming system designed for
deep learning workloads. Although TensorFlow's API exposes
machine learning concepts, internally TensorFlow is a task graph execution engine, making it a good fit for
Task Bench. TensorFlow programs operate via explicit graph construction. Task graphs are composed in Python and run by an
execution engine written in C++. Our Task Bench implementation is straightforward.
